### 2023-07-13 content/submission/plos_revision1/answer_to_reviewers.md

> How was the sanity check performed (as mentioned in the second paragraph of the subsection "Preparation for Analysis")?

The mentioned 'sanity check' was performed manually, e.g. by looking at all the values (mostly the reconstruction parameters), to exclude any operator error.
If errors were spotted at this stage, the reconstructions were deleted and re-done with the correct parameters.
Sometimes errors or problems were only spotted at a later stage, when either the pharyngeal or oral jaws were extracted, or when we noticed that some part of the the whole skull were out of the field of view of the tomographic scan prior to performing the PCA analysis mentioned later in the manuscript.
This means that specifying this as 'sanity check' is more of a glorified wording of telling the readers that we manually looked at the values of each performed tomographic scan to exclude and catch operator errors.
We reworded the sentence to hopefully make this more clear.

### 2023-07-14 content/submission/plos_revision1/answer_to_reviewers.md

> Use the full words, rather than abbreviations, in figure legends for clarity.

Abbreviations in the legends have been written-out (except SI units).
Additionally we added a bit of background information on the specimen to the legend of Fig. 1.

> In the discussion section, the authors mentioned acquiring high-resolution tomographic datasets of a large collection of cichlids.
> However, the statement that "the acquired datasets were imaged over a wide-spanning range of voxel size (3.5–50 μm)" is incorrect.
> The voxel size is specimen-specific, depending on the size of the fish and the chosen parameters.
> Please clarify this point to accurately represent the imaging process.
> The finest resolution was obtained only for small fishes, so specific structures of a fish will have the same image resolution throughout the entire specimen.

The statement over the 'wide-spanning range of voxel sizes' is *not* incorrect, at most---if applied to *one* specimen---imprecise.
The range of voxel sizes is true for the whole study, while---as also correctly noted by the reviewer---the voxel size is specimen- or scan-specific.
We have added a bit of explanatory text to the discussion section.

### 2023-07-14 manuscript.tex
Specify details of stacked scans [ci skip]
This build is based on
https://github.com/habi/EAWAG-manuscript/commit/e3778df7e37340d9ba95d4eabfe433cd259fef1f.

This commit was created by the following CI build and job:
https://github.com/habi/EAWAG-manuscript/commit/e3778df7e37340d9ba95d4eabfe433cd259fef1f/checks
https://github.com/habi/EAWAG-manuscript/actions/runs/5554621680

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...a15f6a93f7f5b262f005c909a8fdcbdf8220da53}{has been updated} since submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/a15f6a93f7f5b262f005c909a8fdcbdf8220da53/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/a15f6a93f7f5b262f005c909a8fdcbdf8220da53}{habi/EAWAG-manuscript@a15f6a9}
on July 13, 2023.

@@

Depending on the size of the specimen we set the X-ray source voltage to 50--80 kV and---depending on the voltage---to a current between 107 and 200 μA.
The X-ray spectrum was filtered either by an aluminum filter of varying thickness (either 0.25, 0.5 or 1 mm for increasing specimen size) before digitization to projection images or recorded in an unfiltered way (for smaller specimen).
Projection images spanning either 180° or 360° of sample rotation were acquired in angular steps of 0.1°, 0.15° or 0.2°, also depending on size of the fish.
In total we recorded 9.8 TB of projection images (\texttt{TIFF} and \texttt{*.iif} files, where the \texttt{*.iif} files are for the so-called alignment scans).

@@

\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
\CSLLeftMargin{15. }
\CSLRightInline{OpenSCAD. {[}cited 13 Jul 2023{]}. Available: \url{https://openscad.org}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wIfTDBqd}{}}%
\CSLLeftMargin{23. }
\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.03.0+6.g08d1f74.dirty documentation. {[}cited 13 Jul 2023{]}. Available: \url{https://image.dask.org/en/latest/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
\CSLLeftMargin{26. }
\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 13 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}

>>>>

\emph{A preprint of this manuscript is available at bioRχiv with the \href{https://doi.org/10.1101/2023.03.30.534917}{doi:10.1101/2023.03.30.534917}.}
\emph{We submitted \href{https://github.com/habi/EAWAG-manuscript/releases/tag/v1.0}{\texttt{v1.0}} (\href{https://habi.github.io/EAWAG-manuscript/v/e1e2ef76a476174a4115937d77457037ddec95df/}{online version}) of the manuscript to \href{https://journals.plos.org/plosone/}{PLOS ONE}.}
\emph{The version you see here \href{https://github.com/habi/EAWAG-manuscript/compare/v1.0...e3778df7e37340d9ba95d4eabfe433cd259fef1f}{has been updated} since submission.}

This manuscript
(\href{https://habi.github.io/EAWAG-manuscript/v/e3778df7e37340d9ba95d4eabfe433cd259fef1f/}{permalink})
was automatically generated
from \href{https://github.com/habi/EAWAG-manuscript/tree/e3778df7e37340d9ba95d4eabfe433cd259fef1f}{habi/EAWAG-manuscript@e3778df}
on July 14, 2023.

@@

Depending on the size of the specimen we set the X-ray source voltage to 50--80 kV and---depending on the voltage---to a current between 107 and 200 μA.
The X-ray spectrum was filtered either by an aluminum filter of varying thickness (either 0.25, 0.5 or 1 mm for increasing specimen size) before digitization to projection images or recorded in an unfiltered way (for smaller specimen).
Projection images spanning either 180° or 360° of sample rotation were acquired in angular steps of 0.1°, 0.15° or 0.2°, also depending on size of the fish.
Since the region of interest (either oral or pharyngeal jaws or the complete skulls of the fish) often did not fit into a single field of view at the voxel size needed to resolve the details needed, we often scanned several stacks along the rotation axis of the specimen in the machine.
These so-called stacked scans are automatically merged to one stack of reconstructions images by the reconstruction software.
In total we recorded 9.8 TB of projection images (\texttt{TIFF} and \texttt{*.iif} files, where the \texttt{*.iif} files are for the so-called alignment scans).

@@

\leavevmode\vadjust pre{\hypertarget{ref-wsjdcTeC}{}}%
\CSLLeftMargin{15. }
\CSLRightInline{OpenSCAD. {[}cited 14 Jul 2023{]}. Available: \url{https://openscad.org}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-wIfTDBqd}{}}%
\CSLLeftMargin{23. }
\CSLRightInline{Image processing with Dask Arrays --- dask-image 2023.03.0+7.g44908b3.dirty documentation. {[}cited 14 Jul 2023{]}. Available: \url{https://image.dask.org/en/latest/}}

@@

\leavevmode\vadjust pre{\hypertarget{ref-rn6XbmFW}{}}%
\CSLLeftMargin{26. }
\CSLRightInline{Teem: nrrd: Definition of NRRD File Format. {[}cited 14 Jul 2023{]}. Available: \url{https://teem.sourceforge.net/nrrd/format.html}}
